## Loading and Summarizing the CPS data
```{r}
CPS=read.csv("~/Downloads/CPSData.csv")
summary(CPS)
str(CPS)
```
## Number of Interviewees in Dataset =131302
## The most common Industry of employment is Educational and health services

```{r}
sort(table(CPS$Region))
sort(table(CPS$State))
```
## State with fewest interviewees = New Mexico
## State with largest interviewees = California
```{r}
table(CPS$Race,CPS$Hispanic)
```
## Races for which there at least 250 Hispanic ethinicity = American Indian,Black,White and Multiracial

## Evaluating Missing Values
```{r}
summary(CPS)
```
## Variables with at least One NA value = MetroAreaCode,Married,Education,EmploymentStatus and Industry

```{r}
table(CPS$Region,is.na(CPS$Married))
table(CPS$Sex,is.na(CPS$Married))
table(CPS$Citizenship,is.na(CPS$Married))
table(CPS$Age,is.na(CPS$Married))

```
## CPS does not ask for marital status for ages 14 and younger. Missing values of Married is related to Age of the interviewee.
## Other variables have missing values and non-missing values for all possible values
```{r}
table(CPS$State,is.na(CPS$MetroAreaCode))
```
## Number of states with people living in non-metropolitan area = 2
## Number of states with people living in metropolitan area = 3
```{r}
tapply(is.na(CPS$MetroAreaCode),CPS$Region,mean)
```
## Midwest has largest population of interviews living in non-metropolitan area
```{r}
tapply(is.na(CPS$MetroAreaCode),CPS$State,mean)
```
## State closest to 30% non-metropolitan population = Wisconsin
## State with largest population of non-metropolitan (ignoring states where all are non-metropolitan)= Montana

##Integrating Metropolitan Area Data
```{r}
MetroAreaMap = read.csv("~/Downloads/MetroAreaCodes.csv")
CountryMap=read.csv("~/Downloads/CountryCodes.csv")
```
```{r}
str(MetroAreaMap)
str(CountryMap)
```
## MetroAreaMap = 271 obs
## CountryMap = 149 obs
```{r}
CPS=merge(CPS,MetroAreaMap,by.x='MetroAreaCode',by.y='Code',all.x=TRUE)
str(CPS)
```
## MetroArea is the new variable that is added
```{r}
summary(CPS$MetroArea)
```
## Number of missing values in MetroArea = 34238
## Boston-Cambridge-Quincy, MA-NH has the largest interviewee population than Atlanta-Sandy Springs-Marietta, GA,Baltimore-Towson, MD and San Francisco-Oakland-Fremont, CA
```{r}
sort(tapply(CPS$Hispanic,CPS$MetroArea,mean))
```
## Laredo,TX has most Hispanic ethnicity
```{r}
sort(tapply(CPS$Race=='Asian',CPS$MetroArea,mean))
```
## The number of metropolitan areas in the United States from which at least 20% of interviewees are Asian = 4

```{r}
sort(tapply(CPS$Education == "No high school diploma", CPS$MetroArea, mean,na.rm=TRUE))
```
## Iowa City, IA has the smallest proportion of interviewees who recevied no school diploma

## Integrating Country of Birth Data
```{r}
CPS =merge(CPS,CountryMap,by.x='CountryOfBirthCode',by.y='Code',all.x=TRUE)
```

```{r}
str(CPS)
```
## Country is added to CPS
```{r}
summary(CPS$Country)
```
## 176 values are missing in Country
```{r}
sort(table(CPS$Country))
```
## Outside North America , Phillipines is the country of birth for  most interviewees
```{r}
sort(tapply(CPS$Country!='United States',CPS$MetroArea=='New York-Northern New Jersey-Long Island, NY-NJ-PA',mean,na.rm=TRUE))
```
## Proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States = 0.3086603
```{r}
sort(tapply(CPS$Country=='India',CPS$MetroArea,mean,na.rm=TRUE))
```
##For India,New York-Northern New Jersey-Long Island, NY-NJ-PA among options


```{r}
sort(tapply(CPS$Country=='Brazil',CPS$MetroArea,mean,na.rm=TRUE))
```
##For Brazil,Boston-Cambridge-Quincy, MA-NH among options
```{r}
sort(tapply(CPS$Country=='Somalia',CPS$MetroArea,mean,na.rm=TRUE))
```
## For Somalia,Minneapolis-St Paul-Bloomington, MN-WI among options