## We'll look at the monthly stock prices of five of these companies: IBM, General Electric (GE), Procter and Gamble, Coca Cola, and Boeing.
```{r}
IBM=read.csv("~/Downloads/IBMStock.csv")
GE=read.csv("~/Downloads/GEStock.csv")
ProcterGamble=read.csv("~/Downloads/ProcterGambleStock.csv")
CocaCola=read.csv("~/Downloads/CocaColaStock.csv")
Boeing=read.csv("~/Downloads/BoeingStock.csv")
```
##Summary
```{r}
str(IBM)
str(GE)
str(ProcterGamble)
str(CocaCola)
str(Boeing)
```
## Each dataframe has 480 observations and two variables, Date and StockProce.

## Summary Statistics

## Converting dates to Date objects
```{r}
IBM$Date = as.Date(IBM$Date, "%m/%d/%y")

GE$Date = as.Date(GE$Date, "%m/%d/%y")

CocaCola$Date = as.Date(CocaCola$Date, "%m/%d/%y")

ProcterGamble$Date = as.Date(ProcterGamble$Date, "%m/%d/%y")

Boeing$Date = as.Date(Boeing$Date, "%m/%d/%y")
```
## Earliest year in dataset
```{r}
summary(IBM$Date)
summary(GE$Date)
summary(ProcterGamble$Date)
summary(CocaCola$Date)
summary(Boeing$Date)
```
## Earliest Year in Dataset=1970
## Latest Year in Dataset=2009
```{r}
summary(IBM)
```
## Mean Stock Price of IBM = 144.38
```{r}
summary(GE)
```
## Mean Stock Price of GE = 59.303
```{r}
summary(CocaCola)
```
## Maximum Stock Price of CocaCola = 60.03
```{r}
summary(Boeing)
```
## Median Stock Price of Boeing = 46.59

```{r}
sd(ProcterGamble$StockPrice)
```
## Standard Deviation of Procter & Gamble = 18.19414

## Visualizing Stock Dynamics
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type='l')

```
## Highest Stock Price = 1973
## Lowest Stock Price = 1980
```{r}
plot(CocaCola$Date,CocaCola$StockPrice,type='l',col='red')
lines(ProcterGamble$Date,ProcterGamble$StockPrice,col='blue',lty=2)
abline(v=as.Date(c("2000-03-01")), lwd=2)

```
## As per the generated plot,Procter&Gamble dropped more than CocaCola
## 1983 : CocaCola going up. CocaCola had lower values
```{r}
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(IBM$Date[301:432],IBM$StockPrice[301:432],col='purple')
lines(GE$Date[301:432],GE$StockPrice[301:432],col='blue')
lines(ProcterGamble$Date[301:432],ProcterGamble$StockPrice[301:432],col='green')
lines(Boeing$Date[301:432],Boeing$StockPrice[301:432],col='orange')
abline(v=as.Date(c("2000-03-01")), lwd=2)
abline(v=as.Date(c("1997-9-01")), lwd=1)
abline(v=as.Date(c("1997-11-01")), lwd=1)

```
## after bubble burst in March 2000, GE dropped the most
## IBM reached the highest value during this time period
## Boeing and PG showed decreasing trend from Sept 1997 to Nov 1997 (Economic crisis in Asia)
## Between 2004 and 2005,Boeing is performing best

## Monthly Trends

```{r}
summary(IBM$StockPrice)
```
## IBM Mean Price = 144.40
```{r}
tapply(IBM$StockPrice,months(IBM$Date),mean)
```
## Jan,Feb,Mar,May,April months had higher monthly mean price than overall average IBM stock price
```{r}
tapply(GE$StockPrice,months(GE$Date),mean)
tapply(ProcterGamble$StockPrice,months(ProcterGamble$Date),mean)
```
## For both GE and PG , April has the highest average stock price.

```{r}
tapply(CocaCola$StockPrice,months(CocaCola$Date),mean)
tapply(Boeing$StockPrice,months(Boeing$Date),mean)
```

## For December ,stock prices are lower than January